\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\rhead{Patient: Santos, Maria E.}
\lhead{Riverside Orthopedic Associates}
\rfoot{Page \thepage}

\definecolor{orthogreen}{RGB}{0,100,60}

\begin{document}

\begin{center}
{\Large\bfseries\color{orthogreen} RIVERSIDE ORTHOPEDIC ASSOCIATES}\\[0.3em]
{\small 800 Professional Plaza, Suite 210, Riverside, CA 92501}\\
{\small Phone: (951) 555-3200 | Fax: (951) 555-3201}\\[1em]
{\LARGE\bfseries OFFICE VISIT NOTE}
\end{center}

\vspace{0.5em}
\hrule height 2pt
\vspace{1em}

\section*{PATIENT INFORMATION}

\begin{tabular}{@{}p{3.5cm}p{5cm}p{3cm}p{4cm}@{}}
\textbf{Patient:} & Maria Elena Santos & \textbf{DOB:} & 03/14/1988 \\
\textbf{Date of Service:} & February 10, 2026 & \textbf{Visit Type:} & New Patient \\
\textbf{Referring MD:} & Dr. Jennifer Walsh (ER) & \textbf{Insurance:} & Hartford WC \\
\textbf{Physician:} & Kevin Park, MD & & \\
\end{tabular}

\vspace{1em}
\hrule
\vspace{1em}

\section*{CHIEF COMPLAINT}

Right wrist fracture sustained in workplace fall on 02/08/2026.

\section*{HISTORY OF PRESENT ILLNESS}

Ms. Santos is a 35-year-old right-hand dominant female carpenter who presents for evaluation of a right distal radius fracture. She fell approximately 15 feet from scaffolding at a construction site on 02/08/2026. She was seen at Riverside General Hospital ER where X-rays revealed a displaced distal radius fracture. Closed reduction was performed and the wrist was placed in a sugar-tong splint.

Patient reports persistent pain at 6/10 despite pain medication. She notes swelling has improved slightly since the ER visit. She denies numbness, tingling, or weakness in her fingers. She is unable to work and has been off work since the injury.

\section*{REVIEW OF SYSTEMS}

\textbf{Positive:} Right wrist pain, difficulty sleeping due to pain, headaches (attributed to concurrent concussion)

\textbf{Negative:} No fever, no chest pain, no numbness/tingling in fingers

\section*{PHYSICAL EXAMINATION}

\textbf{General:} Well-appearing female in no acute distress.

\textbf{Right Upper Extremity:}
\begin{itemize}[nosep]
\item Splint intact, clean, and dry
\item Mild swelling visible at wrist, improved from ER notes
\item Fingers warm, pink, with brisk capillary refill
\item Able to flex/extend all digits against resistance
\item Sensation intact to light touch all digits
\item Radial pulse 2+
\end{itemize}

\section*{IMAGING REVIEW}

Reviewed ER X-rays from 02/08/2026:
\begin{itemize}[nosep]
\item Pre-reduction: Displaced distal radius fracture with 25° dorsal angulation
\item Post-reduction: Acceptable alignment with 5° residual dorsal angulation
\item No involvement of radiocarpal joint
\item Ulnar styloid intact
\end{itemize}

New X-rays obtained today (02/10/2026):
\begin{itemize}[nosep]
\item Alignment maintained
\item No interval displacement
\item Early callus formation not yet visible
\end{itemize}

\section*{ASSESSMENT}

\begin{enumerate}
\item \textbf{Displaced fracture of distal radius, right, post-reduction} - maintaining alignment
\item \textbf{Work-related injury}
\end{enumerate}

\section*{PLAN}

\begin{enumerate}
\item Convert to short arm cast today for improved comfort and stability
\item Cast to remain in place for 4-6 weeks
\item Continue current pain medications as prescribed by ER
\item Follow up in 2 weeks for repeat X-rays
\item \textbf{Work Status: TOTALLY DISABLED} - Patient cannot return to construction work until fracture healed and cleared
\item Refer to hand therapy after cast removal
\item If alignment is lost or patient develops symptoms of carpal tunnel, may need surgical intervention
\end{enumerate}

\section*{WORKERS' COMPENSATION NOTES}

\begin{tabular}{@{}p{5cm}p{9cm}@{}}
\textbf{Date of Injury:} & February 8, 2026 \\
\textbf{Employer:} & Titan Construction LLC \\
\textbf{WC Claim \#:} & HRT-2026-0892147 \\
\textbf{Work Restrictions:} & No use of right hand/arm. No lifting. No driving. \\
\textbf{Estimated Disability:} & 8-12 weeks minimum \\
\textbf{Next Evaluation:} & February 24, 2026 \\
\end{tabular}

\vspace{2em}

\begin{tabular}{@{}p{7cm}p{7cm}@{}}
\hrulefill & \\
\textbf{Kevin Park, MD} & \textbf{Date:} February 10, 2026 \\
Board Certified Orthopedic Surgery & \\
Riverside Orthopedic Associates & \\
\end{tabular}

\vspace{3em}
\hrule
\vspace{1em}

\begin{center}
{\Large\bfseries FOLLOW-UP VISIT NOTE}\\
{\normalsize Date of Service: March 8, 2026}
\end{center}

\vspace{1em}

\section*{INTERVAL HISTORY}

Patient returns for 4-week follow-up. She reports pain has significantly decreased to 2/10. She has been compliant with activity restrictions. Headaches from concussion have resolved. She reports some stiffness in her fingers from immobilization.

\section*{PHYSICAL EXAMINATION}

Cast removed for examination:
\begin{itemize}[nosep]
\item Incision from ER laceration repair well-healed
\item Wrist: Mild residual swelling, tenderness over fracture site minimal
\item ROM: Limited due to 4 weeks of immobilization - expected
\item Grip strength: Reduced compared to left (expected)
\item Neurovascular: Intact
\end{itemize}

\section*{IMAGING}

X-ray right wrist 03/08/2026:
\begin{itemize}[nosep]
\item Fracture healing well with visible callus formation
\item Alignment maintained
\item No hardware (non-surgical management)
\end{itemize}

\section*{ASSESSMENT \& PLAN}

Distal radius fracture - healing appropriately.

\begin{enumerate}
\item Remove cast permanently today
\item Apply removable wrist splint - wear for activities, may remove for hygiene and gentle exercises
\item Begin occupational therapy for ROM and strengthening (prescription provided)
\item OT 2-3x per week for 6-8 weeks
\item \textbf{Work Status: MODIFIED DUTY} - May return to light duty office work only. No lifting over 5 lbs with right hand. No gripping. No construction work.
\item Follow up in 4 weeks
\item Anticipate full release to work in approximately 8-10 more weeks depending on therapy progress
\end{enumerate}

\vspace{2em}

\begin{tabular}{@{}p{7cm}p{7cm}@{}}
\hrulefill & \\
\textbf{Kevin Park, MD} & \textbf{Date:} March 8, 2026 \\
Board Certified Orthopedic Surgery & \\
\end{tabular}

\end{document}
