\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\rhead{MRN: RGH-2026-081547}
\lhead{Riverside General Hospital}
\rfoot{Page \thepage}

\definecolor{medblue}{RGB}{0,82,147}

\begin{document}

\begin{center}
{\Large\bfseries\color{medblue} RIVERSIDE GENERAL HOSPITAL}\\[0.3em]
{\small 500 Medical Center Drive, Riverside, CA 92501}\\
{\small Emergency Department: (951) 555-7000}\\[1em]
{\LARGE\bfseries EMERGENCY DEPARTMENT RECORD}
\end{center}

\vspace{0.5em}
\hrule height 2pt
\vspace{1em}

\section*{PATIENT INFORMATION}

\begin{tabular}{@{}p{3.5cm}p{5cm}p{3cm}p{4cm}@{}}
\textbf{Patient Name:} & Maria Elena Santos & \textbf{MRN:} & RGH-2026-081547 \\
\textbf{DOB:} & 03/14/1988 & \textbf{Age:} & 35 years \\
\textbf{Sex:} & Female & \textbf{Weight:} & 142 lbs \\
\textbf{Address:} & \multicolumn{3}{l}{2847 Maple Grove Dr, Apt 12, Riverside, CA 92501} \\
\textbf{Phone:} & (951) 555-0147 & \textbf{Insurance:} & Hartford WC \\
\end{tabular}

\section*{VISIT INFORMATION}

\begin{tabular}{@{}p{3.5cm}p{5cm}p{3cm}p{4cm}@{}}
\textbf{Date of Visit:} & February 8, 2026 & \textbf{Arrival Time:} & 10:42 AM \\
\textbf{Mode of Arrival:} & EMS/Ambulance & \textbf{Triage Level:} & 2 - Emergent \\
\textbf{Attending MD:} & Dr. Jennifer Walsh & \textbf{Discharge Time:} & 4:35 PM \\
\end{tabular}

\section*{CHIEF COMPLAINT}

Fall from height (approximately 15 feet) at workplace - right wrist pain, head injury, back pain.

\section*{HISTORY OF PRESENT ILLNESS}

35-year-old female construction worker brought in by EMS following a fall from scaffolding at a construction site. Per EMS report, patient fell approximately 15 feet onto concrete floor. Patient was conscious at scene with GCS 14. Patient complains of severe right wrist pain (10/10), headache (7/10), and lower back pain (8/10). Patient denies loss of consciousness but reports feeling ``dizzy'' immediately after the fall. No neck pain. No numbness or tingling in extremities.

\section*{PHYSICAL EXAMINATION}

\textbf{Vital Signs on Arrival:}
\begin{itemize}[nosep]
\item BP: 148/92 mmHg
\item HR: 98 bpm
\item RR: 18/min
\item Temp: 98.4°F
\item SpO2: 99\% on room air
\item Pain: 8/10
\end{itemize}

\textbf{General:} Alert, oriented x3, in moderate distress due to pain.

\textbf{HEENT:} 3cm laceration to right forehead, no active bleeding (controlled at scene). Pupils equal, round, reactive to light. No Battle's sign. No hemotympanum.

\textbf{Neck:} C-spine immobilized per protocol. No midline tenderness on palpation. Full ROM after cleared.

\textbf{Chest:} Clear to auscultation bilaterally. No chest wall tenderness.

\textbf{Cardiovascular:} Regular rate and rhythm, no murmurs.

\textbf{Abdomen:} Soft, non-tender, non-distended.

\textbf{Back:} Tenderness to palpation over L4-L5 region. Paraspinal muscle spasm noted. No step-off deformity.

\textbf{Extremities:}
\begin{itemize}[nosep]
\item Right upper extremity: Obvious deformity of distal radius. Significant swelling and tenderness. Unable to move wrist. Radial pulse intact. Sensation intact to light touch in all digits.
\item Left upper extremity: Abrasion to elbow, ROM intact.
\item Lower extremities: Contusion to left hip, ROM intact bilaterally. Pulses intact.
\end{itemize}

\textbf{Neurological:} GCS 15. Cranial nerves II-XII intact. Motor strength 5/5 all extremities except limited by pain in RUE. Sensation intact.

\section*{DIAGNOSTIC STUDIES}

\textbf{Imaging:}
\begin{itemize}[nosep]
\item \textbf{X-ray, Right Wrist:} Displaced fracture of the distal radius with dorsal angulation. Ulnar styloid intact.
\item \textbf{CT Head without contrast:} No acute intracranial hemorrhage. No skull fracture. No midline shift.
\item \textbf{X-ray, Lumbar Spine:} No acute fracture. Mild degenerative changes at L4-L5.
\item \textbf{CT Cervical Spine:} No acute fracture or dislocation.
\end{itemize}

\textbf{Laboratory:}
\begin{itemize}[nosep]
\item CBC: WNL
\item BMP: WNL
\item Coagulation panel: WNL
\end{itemize}

\section*{ASSESSMENT / DIAGNOSES}

\begin{enumerate}
\item \textbf{Closed displaced fracture, distal radius, right} (S52.501A)
\item \textbf{Concussion without loss of consciousness} (S06.0X0A)
\item \textbf{Lumbar strain} (S39.012A)
\item \textbf{Contusion, left hip} (S70.01XA)
\item \textbf{Laceration, forehead, 3cm} (S01.81XA)
\end{enumerate}

\section*{TREATMENT PROVIDED}

\begin{enumerate}
\item IV access established, normal saline initiated
\item Pain management: Morphine 4mg IV x2
\item Forehead laceration cleaned and closed with 6 sutures (4-0 nylon)
\item Right wrist: Closed reduction performed under conscious sedation. Post-reduction X-ray confirms acceptable alignment. Splinted in sugar-tong splint.
\item Tetanus booster administered
\item Ice packs applied to lumbar region and left hip
\end{enumerate}

\section*{DISPOSITION}

Patient \textbf{discharged home} in stable condition with the following:

\textbf{Discharge Instructions:}
\begin{itemize}[nosep]
\item Concussion precautions provided (written and verbal)
\item Keep splint clean and dry
\item Elevate right arm above heart level when possible
\item Ice lumbar area 20 min every 2 hours while awake
\item Return immediately for: worsening headache, vomiting, vision changes, numbness/tingling, increased pain, fever
\end{itemize}

\textbf{Medications Prescribed:}
\begin{itemize}[nosep]
\item Norco 5/325mg - 1 tablet every 6 hours as needed for pain, \#30
\item Ibuprofen 600mg - 1 tablet every 8 hours with food, \#30
\item Flexeril 10mg - 1 tablet at bedtime for muscle spasm, \#14
\end{itemize}

\textbf{Follow-up:}
\begin{itemize}[nosep]
\item Orthopedic Surgery within 2 days (referral provided)
\item Primary care within 1 week
\item Return to ED if symptoms worsen
\end{itemize}

\vspace{1.5em}

\begin{tabular}{@{}p{7cm}p{7cm}@{}}
\hrulefill & \\
\textbf{Jennifer Walsh, MD} & \textbf{Date/Time:} 02/08/2026 16:35 \\
Emergency Medicine & \\
Riverside General Hospital & \\
\end{tabular}

\end{document}
