\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\rhead{Employee: Santos, Maria E.}
\lhead{Titan Construction LLC - Safety Dept}
\rfoot{Page \thepage}

\definecolor{titanblue}{RGB}{0,51,102}
\definecolor{warningred}{RGB}{180,0,0}

\begin{document}

\begin{center}
{\Large\bfseries\color{titanblue} TITAN CONSTRUCTION LLC}\\[0.3em]
{\small Safety \& Compliance Department}\\
{\small 1200 Commerce Way, Suite 300, Riverside, CA 92507}\\[1em]
{\LARGE\bfseries EMPLOYEE SAFETY TRAINING RECORD}
\end{center}

\vspace{0.5em}
\hrule height 2pt
\vspace{1em}

\section*{EMPLOYEE INFORMATION}

\begin{tabular}{@{}p{4cm}p{10cm}@{}}
\textbf{Employee Name:} & Maria Elena Santos \\
\textbf{Employee ID:} & TC-2022-0147 \\
\textbf{Position:} & Carpenter II \\
\textbf{Department:} & Field Operations \\
\textbf{Hire Date:} & January 15, 2022 \\
\textbf{Supervisor:} & Dave Peterson \\
\end{tabular}

\vspace{1em}

\section*{COMPLETED TRAINING}

\begin{tabular}{@{}p{5cm}p{2.5cm}p{2.5cm}p{4cm}@{}}
\toprule
\textbf{Training Course} & \textbf{Completed} & \textbf{Expires} & \textbf{Status} \\
\midrule
OSHA 10-Hour Construction & 02/01/2022 & N/A & \textcolor{green!60!black}{Current} \\
New Hire Safety Orientation & 01/15/2022 & N/A & \textcolor{green!60!black}{Complete} \\
Hazard Communication (HazCom) & 01/18/2022 & 01/18/2024 & \textcolor{orange}{Due for Refresh} \\
Personal Protective Equipment & 01/18/2022 & 01/18/2024 & \textcolor{orange}{Due for Refresh} \\
Forklift Operator Certification & 03/15/2022 & 03/15/2025 & \textcolor{green!60!black}{Current} \\
First Aid/CPR & 02/01/2022 & 02/01/2024 & \textcolor{red}{EXPIRED} \\
\bottomrule
\end{tabular}

\vspace{2em}

\section*{REQUIRED BUT NOT COMPLETED}

\begin{center}
\fbox{\parbox{0.95\textwidth}{
\begin{center}
\textbf{\color{warningred} \large ! CRITICAL TRAINING GAPS IDENTIFIED !}
\end{center}

\vspace{0.5em}

The following trainings are REQUIRED for Carpenter II position but have \textbf{NO RECORD ON FILE}:

\begin{tabular}{@{}p{6cm}p{4cm}p{4cm}@{}}
\toprule
\textbf{Required Training} & \textbf{OSHA Requirement} & \textbf{Status} \\
\midrule
Fall Protection Training & 29 CFR 1926.503 & \textcolor{red}{\textbf{NOT COMPLETED}} \\
Scaffold User Training & 29 CFR 1926.454 & \textcolor{red}{\textbf{NOT COMPLETED}} \\
Ladder Safety & 29 CFR 1926.1053 & \textcolor{red}{\textbf{NOT COMPLETED}} \\
\bottomrule
\end{tabular}
}}
\end{center}

\vspace{2em}

\section*{TRAINING REQUIREMENT DETAILS}

\subsection*{Fall Protection Training (29 CFR 1926.503)}

\textbf{OSHA Requirement:} The employer shall provide a training program for each employee who might be exposed to fall hazards. The program shall enable each employee to recognize the hazards of falling and shall train each employee in the procedures to be followed in order to minimize these hazards.

\textbf{Employee Exposure:} Maria Santos regularly works at heights exceeding 6 feet, including scaffolding, ladders, and elevated platforms.

\textbf{\color{warningred} Status: NO TRAINING RECORD FOUND}

\textit{Note: A Fall Protection training was scheduled for January 20, 2022 but was cancelled due to weather. It was never rescheduled.}

\subsection*{Scaffold User Training (29 CFR 1926.454)}

\textbf{OSHA Requirement:} The employer shall have each employee who performs work while on a scaffold trained by a person qualified in the subject matter to recognize the hazards associated with the type of scaffold being used and to understand the procedures to control or minimize those hazards.

\textbf{Employee Exposure:} Maria Santos regularly works on scaffolding for drywall installation and finishing.

\textbf{\color{warningred} Status: NO TRAINING RECORD FOUND}

\vspace{2em}

\section*{TRAINING HISTORY LOG}

\begin{tabular}{@{}p{2.5cm}p{5cm}p{3cm}p{3cm}@{}}
\toprule
\textbf{Date} & \textbf{Training} & \textbf{Trainer} & \textbf{Duration} \\
\midrule
01/15/2022 & New Hire Orientation & Sandra Mitchell & 4 hours \\
01/18/2022 & HazCom / PPE & Angela Washington & 2 hours \\
02/01/2022 & OSHA 10-Hour (Day 1) & External - SafetyPro & 5 hours \\
02/02/2022 & OSHA 10-Hour (Day 2) & External - SafetyPro & 5 hours \\
02/01/2022 & First Aid/CPR & External - Red Cross & 4 hours \\
03/15/2022 & Forklift Certification & Mike Chen & 3 hours \\
\midrule
\multicolumn{4}{c}{\textit{No additional training records after March 2022}} \\
\bottomrule
\end{tabular}

\vspace{2em}

\section*{ANNUAL SAFETY TRAINING REQUIREMENTS}

\textbf{Company Policy (Section 5.2):} All field employees shall receive annual refresher training in:
\begin{itemize}[nosep]
\item Fall Protection
\item Scaffold Safety
\item PPE Usage
\item Hazard Communication
\end{itemize}

\textbf{\color{warningred} Finding:} Employee has not received any annual refresher training since initial hire. Last documented safety training was March 15, 2022 (Forklift Certification).

\vspace{2em}

\hrule

\vspace{1em}

\begin{center}
\small\textit{Record compiled by Safety Department on February 12, 2024\\
pursuant to OSHA investigation and Workers' Compensation claim review.}

\vspace{1em}

\textbf{Reviewed by:} Angela Washington, Safety Coordinator\\
\textbf{Date:} February 12, 2024
\end{center}

\end{document}
