\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{array}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\rhead{Case File: WC-2024-TIT-88421}
\lhead{Witness Statements}
\rfoot{Page \thepage}

\begin{document}

\begin{center}
{\LARGE\bfseries WITNESS STATEMENTS}\\[0.5em]
{\large Re: Maria Elena Santos - Workplace Injury}\\[0.3em]
{\normalsize Incident Date: February 8, 2024}\\
{\normalsize Location: Riverside Medical Plaza Construction Site}
\end{center}

\vspace{1em}
\hrule height 2pt
\vspace{2em}

\section*{WITNESS STATEMENT \#1}

\begin{tabular}{@{}p{4cm}p{10cm}@{}}
\textbf{Witness Name:} & Carlos Ramirez \\
\textbf{Position:} & Carpenter \\
\textbf{Employer:} & Titan Construction LLC \\
\textbf{Phone:} & (951) 555-0234 \\
\textbf{Statement Date:} & February 8, 2024 \\
\textbf{Statement Taken By:} & Dave Peterson, Site Foreman \\
\end{tabular}

\vspace{1em}

\noindent\textbf{STATEMENT:}

\begin{quote}
I was working about 20 feet away from Maria on the same floor, installing trim work. I heard her call out and turned around just in time to see her falling. It happened so fast.

I noticed earlier that morning that the guardrails on the east side of her scaffolding section were missing. I remember thinking someone should fix that, but I figured the safety coordinator would catch it. I didn't know Angela wasn't on site that day.

When Maria fell, Jimmy and I ran over immediately. She was lying on the concrete, conscious but in a lot of pain. She was holding her right arm and said her head and back hurt really bad. We told her not to move and Dave called 911 right away.

I've worked with Maria for about a year. She's always careful and follows safety rules. This wasn't her fault - that scaffolding shouldn't have been missing guardrails, and we should have had harnesses for that height.
\end{quote}

\vspace{1em}

\noindent\textbf{Signature:} \underline{\hspace{5cm}} \hfill \textbf{Date:} February 8, 2024

\vspace{3em}
\hrule
\vspace{2em}

\section*{WITNESS STATEMENT \#2}

\begin{tabular}{@{}p{4cm}p{10cm}@{}}
\textbf{Witness Name:} & James ``Jimmy'' O'Brien \\
\textbf{Position:} & Electrician \\
\textbf{Employer:} & Titan Construction LLC \\
\textbf{Phone:} & (951) 555-0345 \\
\textbf{Statement Date:} & February 8, 2024 \\
\textbf{Statement Taken By:} & Dave Peterson, Site Foreman \\
\end{tabular}

\vspace{1em}

\noindent\textbf{STATEMENT:}

\begin{quote}
I was running wire through the ceiling about 30 feet from where Maria was working. I heard a noise - like wood sliding - and then Maria screamed. I looked over and saw her falling off the scaffolding.

She hit the ground hard. It was a bad fall, probably 15 feet at least. Carlos and I got to her in seconds. She was awake but clearly hurt. Her wrist was bent at a weird angle and she had a cut on her forehead that was bleeding.

I want to say that I've complained before about safety issues on this site. Just last week I mentioned to Dave that some of the scaffolding planks looked loose. I don't know if anyone checked them. And I know for a fact we haven't had a real safety meeting in at least a month.

Maria's a good worker. She didn't do anything wrong. The scaffolding was set up wrong - no guardrails on one side and the planks weren't secured properly.
\end{quote}

\vspace{1em}

\noindent\textbf{Signature:} \underline{\hspace{5cm}} \hfill \textbf{Date:} February 8, 2024

\vspace{3em}
\hrule
\vspace{2em}

\section*{WITNESS STATEMENT \#3}

\begin{tabular}{@{}p{4cm}p{10cm}@{}}
\textbf{Witness Name:} & Angela Washington \\
\textbf{Position:} & Safety Coordinator \\
\textbf{Employer:} & Titan Construction LLC \\
\textbf{Phone:} & (951) 555-0456 \\
\textbf{Statement Date:} & February 9, 2024 \\
\textbf{Statement Taken By:} & Sandra Mitchell, HR Director \\
\end{tabular}

\vspace{1em}

\noindent\textbf{STATEMENT:}

\begin{quote}
I was not present at the Riverside Medical Plaza site on February 8, 2024. I had been assigned to cover our downtown site that day because their safety coordinator was out sick. I was not informed that someone else would need to cover my inspection duties at the Riverside site.

Normally, I perform scaffolding inspections at the start of each shift, per OSHA requirements. I inspect all scaffolding for proper guardrails, secured planks, and stable base conditions. I also verify that workers have access to fall protection equipment.

I last inspected the scaffolding in Building C on February 7, 2024. At that time, all guardrails were in place. I do not know why they were removed or who removed them between my last inspection and the accident.

I have raised concerns multiple times about the lack of a backup safety coordinator when I am reassigned to other sites. This concern was documented in emails to my supervisor, Michael Chen, dated January 15, 2024 and January 28, 2024.

I feel terrible about what happened to Maria. This accident could have been prevented if proper safety protocols had been followed and if coverage had been arranged for my absence.
\end{quote}

\vspace{1em}

\noindent\textbf{Signature:} \underline{\hspace{5cm}} \hfill \textbf{Date:} February 9, 2024

\vspace{2em}

\begin{center}
\rule{10cm}{0.4pt}\\[1em]
\small\textit{All statements collected pursuant to workplace injury investigation.\\
Copies provided to Workers' Compensation carrier and legal counsel.}
\end{center}

\end{document}
